25 years of Social Work Research

### 2015-02-22 dataCleaning.Rmd
Journal title corrections

full.df$record <- ifelse(full.df$record ==
    "Aretê",                                   #Spelling difference
      "Arete",
              full.df$record)
```

>>>>

full.df$record <- ifelse(full.df$record ==
    "Aretê",                                   #Spelling difference
      "Arete",
              full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Journal of Gay and Lesbian Social Services",     #Spelling difference
        "Journal of Gay & Lesbian Social Services",
                        full.df$record)

full.df$record <- ifelse(full.df$record ==
    "Canadian Social Work Review/Revue canadienne de service social",
        "Canadian Social Work Review",
                        full.df$record)
```
